ms_0_intro

### 2017-08-18 man/ms_0_intro.Rmd
update

>>>>

Althought several works have reported these two years as some of the worst drought events, we characterised the drought at several spatio-temporal scales in the study area. From a long-term perspective, we compare the accumulated monthly precipitation at a meteorological station (Granada, Base Aérea) during the hydrological years 2004-2005 and 2011-2012 with the average of accumulated monthly precipitation for the period 1950-2015.
